MSDS 6372 Project 1 Objective 2

### 2020-02-11 Codebooks/MSDS6372.Project.O1.Rmd

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
library(devtools)
options(scipen=999)
```

@@

nyc.bins$reviewsBin <- var.bin(nyc.bins$number_of_reviews, bins = 50)
nyc.bins$nightsBin <- var.bin(nyc.bins$minimum_nights, bins = 50)
nyc.bins$availBin <- var.bin(nyc.bins$availability_365, bins = 50)
nyc.bins$listBin <- var.bin(nyc.bins$calculated_host_listings_count, bins = 10)

nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365"))
invisible(nyc.bins)
```

@@

```{r intuitive model}
#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared

rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfit)
plot(rfit)

rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
summary(rfitl)
plot(rfitl)
```

@@

#predict.regsubsets =function (object , newdata ,id ,...){
#  form=as.formula (object$call [[2]])
#  mat=model.matrix(form ,newdata )
#  coefi=coef(object ,id=id)
#  xvars=names(coefi)
#  mat[,xvars]%*%coefi
#}

#testASE<-c()
#note my index is to 20 since that what I set it in regsubsets
#for (i in 1:20){
#  predictions<-predict.regsubsets(object=reg.fwd,newdata=test,id=i) 
#  testASE[i]<-mean((log(test$AvgWinnings)-predictions)^2)
#}

#par(mfrow=c(1,1))
#plot(1:20,testASE,type="l",xlab="# of predictors",ylab="test vs train ASE",ylim=c(0.2,0.8))

#index<-which(testASE==min(testASE))
#points(index,testASE[index],col="red",pch=10)
#rss<-summary(reg.fwd)$rss
#lines(1:20,rss/100,lty=3,col="blue")  #Dividing by 100 since ASE=RSS/sample size

#coef(reg.final,XXXX)

#final.model<-lm(log(AvgWinnings)~Greens+AvgPutts+Save,data=golf)
#summary(final.model)
```

```{r backward selection model}
nyc.bck = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="backward", data=log.nyc, nvmax=20)
summary(nyc.bck)$adjr2
#summary(nyc.bck)$rss
#summary(nyc.bck)$bic
```

```{r seqrep selection model}
nyc.seq = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="seqrep", data=log.nyc, nvmax=20)
summary(nyc.seq)$adjr2
#summary(nyc.seq)$rss
#summary(nyc.seq)$bic
```

@@

```{r Assumptions Check on Intuitive Model}
par(mfrow=c(2,2))
full.model<-lm(price~.,data=nyc4)
plot(full.model)
```

@@

>>>>

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
library(devtools)
library(leaps)
options(scipen=999)
```

@@

nyc.bins$reviewsBin <- var.bin(nyc.bins$number_of_reviews, bins = 50)
nyc.bins$nightsBin <- var.bin(nyc.bins$minimum_nights, bins = 50)
nyc.bins$availBin <- var.bin(nyc.bins$availability_365, bins = 50)
nyc.bins$listBin <- var.bin(nyc.bins$calculated_host_listings_count, bins = 10)
nyc.bins$tsquBin <- var.bin(nyc.bins$tsquare_distance, bins = 20)

nyc.bins <- select(nyc.bins,-c("minimum_nights", "number_of_reviews", "calculated_host_listings_count", "availability_365", "tsquare_distance"))
invisible(nyc.bins)
```

@@

```{r intuitive model}
#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfit)
plot(rfit)
rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
summary(rfitl)
plot(rfitl)
```

@@

fwd.adjr2 <- summary(nyc.fwd)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
fwd.index <- which(adjr2 == max(adjr2))
points(fwd.index, adjr2[fwd.index],col="red", pch=10)
```

- Below are the final coeffecients based on the above forwad selection model with highest Adjusted r-squared at 15

```{r}
coef(nyc.fwd,15)
```

```{r backward selection model}
nyc.bck = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="backward", data=log.nyc, nvmax=20)
summary(nyc.bck)$adjr2

bck.adjr2 <- summary(nyc.bck)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bck.index <- which(adjr2 == max(adjr2))
points(bck.index, adjr2[bck.index],col="red", pch=10)
```

- Below are the final coeffecients based on the above backward selection model with highest Adjusted r-squared at 15

```{r}
coef(nyc.bck,15)
```

```{r seqrep selection model}
nyc.seq = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="seqrep", data=log.nyc, nvmax=20)
summary(nyc.seq)$adjr2

bck.adjr2 <- summary(nyc.bck)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bck.index <- which(adjr2 == max(adjr2))
points(bck.index, adjr2[bck.index],col="red", pch=10)
```

@@

### XXXXXXXX

```{r Assumptions Check on Intuitive Model}
par(mfrow=c(2,2))
full.model<-lm(price~.,data=nyc4)
plot(XXXXXXX)
```

@@

### XXXXXXXXX

### 2020-02-11 Codebooks/MSDS6372.Project.O2.Rmd

---
title: "MSDS 6372 Project 1 Objective 1"
author: "Jaclyn A Coate"
date: "2/5/2020"
output: html_document
---

@@

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
library(devtools)
library(leaps)
options(scipen=999)
```

# Objective 1:
## Question of Interest: what variables are used to predict price of a NYC Airbnb

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_1/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

@@

#### Zero variance variable check - all show variance so remain in model

#```{r zero variable check}
#Results show no zero variance variables, leave in all
#skim(nyc3)
#```

@@

#### Modeling
- We are not seeing any linear correlation between the dependent and independent numeric varaibles
  - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
- We are seeing a strong linear correlation between the dependent and independent categorical variables
- We have surfaced the best residuals assumptions matched in a log-linear model
  - Due to this we are moving forward with modeling a log-linear model with singular variables as well as all interaction terms
  - This is to add complexity to our model, we have a low number of varaibles to select from
    - In adding this complexity we are tryign to surface any possible linear variable interations that may contribute to our model
    - If these are surfaced we will go back and use graphical means to verify the model's discovery

```{r full model check}
nyc.model = lm(lprice~neighbourhood + room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + tsquare_distance, data=log.nyc)
summary(nyc.model)

#Surfacing only significant neighborhoods
nyc.model2 = tidy(nyc.model)
options(scipen = 999)
invisible(nyc.model2)
nyc.modeldf <- nyc.model2[nyc.model2$p.value < 0.05,]
invisible(view(nyc.modeldf))
```

```{r}
#would reducing the data set to just sig values help?
```

#### Model selection attempts

```{r intuitive model}
#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfit)
plot(rfit)
rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
summary(rfitl)
plot(rfitl)
```

```{r forward selection model}
nyc.fwd = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method = "forward", data=log.nyc, nvmax=20)
summary(nyc.fwd)$adjr2

fwd.adjr2 <- summary(nyc.fwd)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
fwd.index <- which(adjr2 == max(adjr2))
points(fwd.index, adjr2[fwd.index],col="red", pch=10)
```

- Below are the final coeffecients based on the above forwad selection model with highest Adjusted r-squared at 15

```{r}
coef(nyc.fwd,15)
```

```{r backward selection model}
nyc.bck = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="backward", data=log.nyc, nvmax=20)
summary(nyc.bck)$adjr2

bck.adjr2 <- summary(nyc.bck)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bck.index <- which(adjr2 == max(adjr2))
points(bck.index, adjr2[bck.index],col="red", pch=10)
```

- Below are the final coeffecients based on the above backward selection model with highest Adjusted r-squared at 15

```{r}
coef(nyc.bck,15)
```

```{r seqrep selection model}
nyc.seq = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, method="seqrep", data=log.nyc, nvmax=20)
summary(nyc.seq)$adjr2

bck.adjr2 <- summary(nyc.bck)$adjr2
plot(1:20, adjr2, type = "l", ylab = "Adjusted R-squared", xlab = "# Of Predictors")
bck.index <- which(adjr2 == max(adjr2))
points(bck.index, adjr2[bck.index],col="red", pch=10)
```

```{r exhaustive selection model}
#Due to an exhaustive method being too large. We are commenting out this model and moving forward with selective methods that will run
#nyc.exh = regsubsets(lprice~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365, data=log.nyc, nvmax=20)
#summary(nyc.exh)$adjr2
#summary(nyc.exh)$rss
#summary(nyc.exh)$bic
```

#### Assumptions Check on Intuitive Model
- Residuals near normally distributed but still skewed
- Envoking Central Limit Theorum due to such a large sample size
- Constant Variance
  - The QQ Plot shows an extreme deviation from normality. Even with the Central Limit Theorum we do not feel comforablte moving forward.

### XXXXXXXX

```{r Assumptions Check on Intuitive Model}
par(mfrow=c(2,2))
full.model<-lm(price~.,data=nyc4)
plot(XXXXXXX)
```

#### Assumptions Check on Log-Linear Intuitive Model
- Risduals are near normally distributed with them being slightly off
  - Envoking Central Limit Theorum due to such a large sample size
  - Passed
- Constant variance
  - The QQ-plot is showing much less departure from normality
  - Passed

### XXXXXXXXX

```{r Assumptions Check on Log-Linear Intuitive Model}
par(mfrow=c(2,2))
log.depend.model<-lm(lprice~.,data=log.nyc)
plot(log.depend.model)
```

- Independence
  - Assumed
  - Passed
- Multicollinearity
  - We are seeing a high VIF for our distance to Times Square

```{r Multicollinearity Assumption on Log-Linear Intuitive Model}
vif(log.depend.model)[,3]^2
```

#### MLR May Not Be The Best
- Multiple linear regression is just one option in building a predictive model for a continuous response
- We are seeing it as a bad option because
  - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
    - We have gotten close, but we have worked extremely hard in specifying our model and manipulating the raw data to surface a linear relationship
    - This makes the interpretation into the real world application difficult to interpret
  - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
    - These options are less time consuming because the model complexity is built into the lagorithm
    - We also do not have to specify how a relationship exists ahead of time
- Since we see a strong relationship between the categorical variables, we move forward with a Two-Way ANOVA model to create a model way predict the price of a NYC AirBnB.

>>>>

---
title: "MSDS 6372 Project 1 Objective 2"
author: "Jaclyn A Coate"
date: "1/22/2020"
output:
  html_document: default
  word_document: default
---

@@

```{r libraries}
library(tidyverse)
library(mice)
library(skimr)
library(corrplot)
library(car)
library(ISLR)
library(ggplot2)
library(gridExtra)
library(SamplingStrata)
library(rbin)
library(leaps)
library(dplyr)
library(ggplot2)
library(geosphere)
library(broom)
library(plyr)
library(devtools)
options(scipen=999)
```

# Objective 2 EDA:

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
nrow(nycraw)
```

@@

@@

#### Modeling
- We are not seeing any linear correlation between the dependent and independent numeric varaibles
  - We have tried: linear regression, log-linear regression transformation, log-log regression transformation, binning, and outlier drop.
- We are seeing a strong linear correlation between the dependent and independent categorical variables
- We have surfaced the best residuals assumptions matched in a log-linear model
  - Due to these discoveries we are moving forward with a Two-Way ANOVA in order to create the strongest model
- The number of Neighborhoods is so high deriving any sort of practical significance in a two-way ANOVA would be too difficult. 
  - Changing our selected variables to Neighbourhod_Group and room_type

#### Clean data for Two-Way ANOVA

```{r data prep2}
nyc.anova.raw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nyc.anova.raw)
nyc.anova.raw2 <- select(nyc.anova.raw, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood", "minimum_nights", "number_of_reviews", "last_review", "reviews_per_month", "calculated_host_listings_count", "availability_365"))
head(nyc.anova.raw2)

nyc.anova.raw2 <- filter(nyc.anova.raw2, price >= 25 & price <= 400)
invisible(view(nyc.anova.raw2))
```

## Start 2-Way ANOVA Analysis
- In completing this project with the tools learned in Unit 3 - we will perform a 2-Way ANOVA analysis.

#### Summary Statistics Table
- Creating Mean, SD, SE, Min, Max, and IQR
- Table of graphable statistics

```{r attach data create function sumstats table}
nyc.anova <- nyc.anova.raw2

#Attaching the data set
attach(nyc.anova)
#Creating a function
nycsummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/sqrt(length(x)), min(x), max(x), IQR(x))
  names(result)<-c("N","Mean","SD","SE","Min","Max","IQR")
  return(result)
}
#Creating a summary stats table
nycsumstats<-aggregate(price~neighbourhood_group*room_type,data=nyc.anova,nycsummary)
nycsumstats<-cbind(nycsumstats[,1:2],nycsumstats[,-(1:2)])
nycsumstats
```

#### Summary Statistics Graph
#- The below graph shows characteristics of a nonadditive model
#- Next Steps:
#  1. Fit a non-additive model
#  2. Check the assumptions
#  3. Exmine Type III Sum of Squares F-test tables

```{r sumstats graph}
ggplot(nycsumstats,aes(x=room_type,y=Mean,group=neighbourhood_group,colour=neighbourhood_group))+
  ylab("NYC AirBnBs Prices")+xlab("Room Type")+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=Mean-SD,ymax=Mean+SD),width=.1)
```

#### Nonadditive 2-Way ANOVA
- QQ Plot for assumption assessment
  - Show a curve, needs transformation

```{r nonadditive model assumptions check}
#The following code fits the nonadditive two way anova model and then produces the first the main residual diagnostics for assumption checking
nyc.model.fit<-aov(price~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.anova)

nyc.fits <- data.frame(fitted.values=nyc.model.fit$fitted.values,residuals=nyc.model.fit$residuals)

#Reisudals vs Fitted
nyc.plot1 <- ggplot(nyc.fits, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
  xlab("Predicted")+geom_point()
#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
nyc.plot2 <- ggplot(nyc.fits,aes(sample=residuals))+
  stat_qq()+geom_abline(intercept=mean(nyc.fits$residuals), slope = sd(nyc.fits$residuals))
#Histograms of residuals
nyc.plot3 <- ggplot(nyc.fits, aes(x=residuals)) + 
  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
  geom_density(alpha=.1, fill="red")
#Grid of all 3 graphs above
grid.arrange(nyc.plot1, nyc.plot2, nyc.plot3, ncol=3)
```

```{r nonadditive assumptions check 2}
par(mfrow=c(2,2))
plot(nyc.model.fit)
```

#### Log transformation on price

```{r log transformation on price}
#Transforming price to logged variable
nyc.log.anova <- nyc.anova %>% mutate(lprice=log(price))
#view(nyc.final)
```

#### Assumptions check on log transformation of price
- Equal variances: there is some slight variation of variances but this will suffice in order to move forward
- QQ Plot: there is still some slight departure from normality, but again this is acceptable to move forward with our model
- DON'T FORGET TO MENTION CLT - Central Limit Theorum

```{r nonadditive log assumptions check}
nyc.model.fit.log<-aov(lprice~neighbourhood_group+room_type+neighbourhood_group:room_type,data=nyc.log.anova)

nyc.fits.log <- data.frame(fitted.values=nyc.model.fit.log$fitted.values,residuals=nyc.model.fit.log$residuals)

#Reisudals vs Fitted
nyc.logplot1 <- ggplot(nyc.fits.log, aes(x=fitted.values,y=residuals))+ylab("Residuals")+
  xlab("Predicted")+geom_point()
#QQ Plot of residuals #Note the diagonal abline is only good for qqplots of normal data
nyc.logplot2 <- ggplot(nyc.fits.log,aes(sample=residuals))+
  stat_qq()+geom_abline(intercept=mean(nyc.fits.log$residuals), slope = sd(nyc.fits.log$residuals))
#Histograms of residuals
nyc.logplot3 <- ggplot(nyc.fits.log, aes(x=residuals)) + 
  geom_histogram(aes(y=..density..),binwidth=1,color="black", fill="gray")+
  geom_density(alpha=.1, fill="red")
#Grid of all 3 graphs above
grid.arrange(nyc.logplot1, nyc.logplot2, nyc.logplot3, ncol=3)
```

par(mfrow=c(2,2))
```{r non additive log assumptions check2}
plot(nyc.model.fit.log)
```

#### Outliers
- Since there are not singular points that are aggressively skewing the data, these outliers aren't considered unique or affecting the model in a way that would not be logical.
- Choose to leave all low and high end metrics since the model should take these into account

#### Type III F-test table
- From the below F-test table we can see that neighborhood_group, room_type, as well as their interaction are all statistically significant for this model
- The type-3 sums of squares F-test is provided below. The test for an interaction is not significant (F-stat: 12.493 p-value < .0001). Therefore, we can conclude that the potential changes in AirBnB price for one of the factors does depend on the other.

```{r Ftest}
Anova(nyc.model.fit, type = 3)
```

```{r log Ftest}
Anova(nyc.model.fit.log,type=3)
```

```{r ftest CIs}
#Confidence Intervals for F Test
confint(nyc.model.fit.log)
```

#### Multiple Test Technique on No Transformation: Tukey-Kramer
- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
- Move forward with the Tukey-Kramer to discover what factors and/or combinations contribute to predicting the price of a NYC AirBnB

```{r adjp tukey}
nyc.anova.diff <- TukeyHSD(nyc.model.fit,"neighbourhood_group:room_type", conf.level = .95)
nyc.anova.diff
```

```{r adjup tukey graph}
plot(TukeyHSD(nyc.model.fit,"neighbourhood_group:room_type", conf.level = .95))
```

```{r sig pvalues}
nyc.anova.diff2 = tidy(nyc.anova.diff)
colnames(nyc.anova.diff2)[3] <- "diff"
invisible(view(nyc.anova.diff2))

nyc.anova.diffdf <- nyc.anova.diff2[nyc.anova.diff2$adj.p.value <0.05,]
nyc.anova.diffdf <- nyc.anova.diffdf[order(nyc.anova.diffdf$diff),]
nyc.anova.diffdf
```

#### Multiple Test Technique on Log Transformationl: Tukey-Kramer
- From the F-test table we can see that all current variables are statistically significnat at the 0.05 alpha level
- Move forward with the Tukey-Kramer to discover what factors and/or combinations contribute to predicting the price of a NYC AirBnB

```{r log tukey pvalues}
#nyc.anova.log.diff <- TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95)
#nyc.anova.log.diff
```

```{r log tukey plot CI}
#plot(TukeyHSD(nyc.model.fit.log,"neighbourhood_group:room_type", conf.level = .95))
```

#### Back Transformation
- To keep the data easily interpretable we have moved our nyc.anova.diff results into a data frame and are now going to back transform the diff and upper and lower confidence interval results.

```{r log back transformation}
#nyc.anova.log.diff2 = tidy(nyc.anova.log.diff)
#colnames(nyc.anova.log.diff2)[3] <- "diff"
#invisible(view(nyc.anova.log.diff2))

#nyc.anova.log.diffdf <- nyc.anova.log.diff2[nyc.anova.log.diff2$adj.p.value <0.05,]
#invisible(yc.anova.log.diffdf)

#ConfInt_Diff_Backlog <- yc.anova.log.diffdf %>% mutate(Tdiff = exp(diff))
#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog %>% mutate(Tlow = exp(conf.low))
#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog %>% mutate(Thigh = exp(conf.high))

#ConfInt_Diff_Backlog <- select(ConfInt_Diff_Backlog, -c("diff", "conf.low", "conf.high"))
#ConfInt_Diff_Backlog <- ConfInt_Diff_Backlog[order(-ConfInt_Diff_Backlog$Tdiff),]
#ConfInt_Diff_Backlog
```
